\documentclass[a4paper,10pt]{article}
\usepackage[margin=0.7in]{geometry}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{titlesec}
\usepackage{parskip}

% Formatting
\setlist[itemize]{noitemsep, topsep=0pt}
\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]
\pagestyle{empty}

\begin{document}

\begin{center}
    {\LARGE \textbf{Nathan Johnson}}\\
    Chicago, Illinois \,|\, \href{mailto:njohnson14@luc.edu}{njohnson14@luc.edu} \,| 
    \href{https://github.com/nathanjohnsongithub}{GitHub} \,|\, \href{https://www.linkedin.com/in/nathan-johnson-compsci/}{LinkedIn}
\end{center}

\section*{Education}
\textbf{Loyola University of Chicago} \hfill Chicago, IL\\
\textit{Bachelor of Science in Computer Science} \hfill Expected May 2026\\
\textbf{GPA:} 3.92\\
\textbf{Relevant Coursework:} Data Structures and Algorithms, Discrete Math, Calculus I \& II, Linear Algebra, Computer Systems, Programming Languages, Operating Systems, Object-Oriented Design, Machine Learning, Software Engineering\\
\textbf{Future Coursework:} Database Programming, NLP

\section*{Experience}

\textbf{Enova International} \hfill Chicago, IL\\
\textit{Software Engineering Intern} \hfill June 2025 -- August 2025
\begin{itemize}
    \item Completed a Software Engineering internship in the Small and Medium Business Engineering Department, contributing to the modernization of legacy systems through cloud-native design.
    \item Migrated core business functionalities into a scalable microservice architecture leveraging Go, AWS Lambda, Salesforce Apex, and Terraform.
    \item Collaborated with cross-functional teams to deliver production-ready, fault-tolerant solutions that streamlined operations and supported long-term platform growth.
\end{itemize}

\vspace{0.5em}

\textbf{Argonne National Laboratory} \hfill Lemont, IL\\
\textit{Computational Research Aide | Sophomore} \hfill May 2024 -- August 2024
\begin{itemize}
    \item Contributed to performance-critical HPC applications (ARCHES project) by offloading GPU computations with SYCL.
    \item Optimized parallel workloads using OpenMP, improving scalability and efficiency across large clusters.
    \item Conducted profiling (MAQAO) to identify bottlenecks and implemented multi-threaded optimizations.
\end{itemize}

\vspace{0.5em}

\textit{Computational Research Aide} \hfill May 2023 -- August 2023
\begin{itemize}
    \item Developed Python-based HPC workflows and integrated C/C++ libraries for performance-critical modules.
    \item Employed cProfile and mpi4py for benchmarking and parallel computing, enhancing performance across distributed systems.
\end{itemize}

\vspace{0.5em}

\textbf{TrueLayer} \hfill London, UK\\
\textit{Business Development Intern} \hfill January 2025 -- Present
\begin{itemize}
    \item Gained hands-on experience at a leading FinTech provider of Pay by Bank, Open Banking, and A2A solutions.
    \item Analyzed data and identified strategic commercial opportunities to grow partnerships in a fast-paced environment.
    \item Collaborated cross-functionally with technical and non-technical teams, reinforcing communication and problem-solving skills.
\end{itemize}

\vspace{0.5em}

\textbf{Loyola University of Chicago} \hfill Chicago, IL\\
\textit{Loyola AI Club President} \hfill August 2023 -- December 2024
\begin{itemize}
    \item Led a machine-learning movie recommendation project utilizing Pandas, NumPy, and Scikit-learn.
    \item Organized and presented weekly meetings, competitions, and guest speaker events to expand club engagement.
    \item Demonstrated leadership and communication skills while growing the club’s active membership base.
\end{itemize}

\section*{Skills}
\textbf{ Programming:} Python, Go, C++, Java, Scala, Ruby, Apex\\
\vspace{0.25em}
\textbf{Frameworks \& Technologies:} AWS, Terraform, Salesforce, Linux, Git, REST APIs\\
\vspace{0.25em}
\textbf{Data \& Machine Learning:} Pandas, NumPy, Scikit-learn, Data Analysis\\
\vspace{0.25em}
\textbf{High-Performance Computing:} OpenMP, SYCL, mpi4py, Parallel Optimization\\
\vspace{0.25em}
\textbf{Professional Skills:} Software Design, Systems Thinking, Communication, Leadership
Collaboration


\end{document}
